---
title: "R Notebook"
output: html_notebook
---

# Benjamini-Hochberg (BH) procedure - Used to calculate q-values for multiple hypothesis tests.

```{r}
# Generate a vector of p-values
p_values <- c(0.05, 0.01, 0.002, 0.008, 0.07, 0.03)

# Perform the BH procedure
q_values <- p.adjust(p_values, method = "BH")

# Print the results
print(q_values)
```
# Storey-Tibshirani (ST) procedure - An alternative to the BH procedure that is more powerful in certain situations.

```{python}
import numpy as np
from statsmodels.stats.multitest import fdrcorrection

# Generate a numpy array of p-values
p_values = np.array([0.05, 0.01, 0.002, 0.008, 0.07, 0.03])

# Perform the ST procedure
q_values = fdrcorrection(p_values, alpha=0.05, method='indep')[1]

# Print the results
print(q_values)
```

# two-sample t-test in Python:
```{python}
import scipy.stats as stats

# Generate two sets of data
group1 = [10, 12, 14, 16, 18]
group2 = [9, 11, 13, 15, 17]

# Perform the t-test
t_stat, p_value = stats.ttest_ind(group1, group2)

# Print the results
print("t-statistic:", t_stat)
print("T-test p-value:", p_value)
```

# wilcox test

```{python}
from scipy.stats import wilcoxon

# Perform Wilcoxon signed-rank test
statistic, p_value = wilcoxon(group1, group2)

# Print the test statistic and p-value
print('Test statistic:', statistic)
print('Wilcoxon p-value:', p_value)
```


# chi-squared test - Used to determine if there is a significant difference between the observed and expected frequencies of categorical data.

```{r}
# Generate a contingency table
table <- matrix(c(25, 10, 15, 20), nrow = 2, ncol = 2)
rownames(table) <- c("Male", "Female")
colnames(table) <- c("Smoker", "Non-smoker")
table

# Perform the chi-squared test
result <- chisq.test(table)

# Print the results
print(result)
```
# correlation test

```{python}
import pandas as pd

# Create a DataFrame with multiple columns
df = pd.DataFrame({'x': [1, 2, 3, 4, 5], 'y': [10, 20, 30, 40, 50], 'z': [5, 4, 3, 2, 1]})

# Calculate the correlation between the two columns
corr = df['x'].corr(df['z'])

# Print the correlation coefficient
print('Correlation coefficient:', corr)

# Compute the correlation matrix
corr_matrix = df.corr()

# Print the correlation matrix
print('Correlation matrix:\n', corr_matrix)
```

